### 2013-01-12 paper.tex
first commit

\documentclass[12pt]{article}

% This first part of the file is called the PREAMBLE. It includes
% customizations and command definitions. The preamble is everything
% between \documentclass and \begin{document}.

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath}               % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments
\usepackage{amssymb}

% various theorems, numbered by section

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{defn}[thm]{Definition}

\DeclareMathOperator{\id}{id}

\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
\newcommand{\RR}{\mathbb{R}}      % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}

\begin{document}

\nocite{*}

\title{Algebraic Topology Final Report: Morse Theory}

\author{Shih-Kai Chiu \\
r01221031}

\maketitle

\begin{abstract}
  This report covers roughly the part I of J. Milnor's book(citation). The main
  result is the theorem of Morse: every smooth manifold has the same homotopy
  type of a CW-complex. We prove this theorem by developing the concept of
  non-degenerate smooth functions, their index at critical points and the
  correspondence between the index and the dimension of attaching cells. After
  the main theorem, the existence of non-degenerate smooth functions on
  manifolds is established, and as an application, an alternating proof of the
  Lefschetz hyperplane theorem is given.
\end{abstract}

\section{Basic Definitions and Lemmas}

\subsection{Attaching Cells}

Let $Y$ be any topological space, and let
\begin{equation}
  e^k = \{ x \in \RR^k | \left| x \right| < 1 \}
\end{equation}
be the k-cell. The boundary
\begin{equation}
  \dot{e}^k = \{ x \in \RR^k | \left| x \right| = 1 \}
\end{equation}
is the (k-1)-sphere, $S^{k-1}$. Specifically, we put $e^0$ as a point and set
$\dot{e}^0 = \emptyset$. We call a continuous map $g: S^{k-1} \to Y$ an
attaching map and obtain a new topological space
\begin{equation}
  Y \cup_g e^k
\end{equation}
by identifying each $x \in \dot{e}^k$ with $g(x) \in Y$.

\subsection{Non-degenerate critical points}

Let $M^n$ be a smooth manifold of dimension $n$, and let $f: M \to \RR$ be a
smooth function on $M$. We recall that a point $x \in M$ is called a critical
point of $f$ if the differential map $ df_p : T_pM \to \RR $ is singular. This
is equivalent to $\frac{\partial f}{\partial x^i} (p) = 0$ for all $i = 1,
.. ,k$ and any local coordinate $(x^1, .., x^k)$, since the map $df_p$ in local
coordinate is a row matrix with a non-empty kernel.

\begin{defn}
  (Non-degenerate critical point) Let $p \in M$ and let $(x^1, .., x^k)$ be a
  local coordinate at $p$. $p$ is called a non-degenerate critical point of $f$
  if
  \begin{equation}
    \left( \frac{\partial^2 f}{\partial x^i \partial x^j} (p) \right)
  \end{equation}
  is an invertible matrix. On the other hand, $p$ is a called degenerate
  critical point if the matrix is singular.
\end{defn}

The definition above is independent of local coordinates. For, if $(x^1, ..,
x^k)$ and $(y^1, .., y^k)$ are two local coordinates at $p$, then
\begin{equation}
      \left( \frac{\partial^2 f}{\partial y^k \partial y^l} (p) \right) =
      J^T\left( \frac{\partial^2 f}{\partial x^i \partial x^j} (p) \right)J,
\end{equation}
where $J = \left( \frac{\partial x^i}{\partial y^j}(p) \right)_{i,j}$ is the
coordinate change matrix, which is non-singular.

\section{Homotopy Type in Terms of Critical Values}

Let $M$ be a smooth manifold of dimension $k$. By Whitney Embedding Theorem, we
can embed $M$ into $\RR^n, n > k$. Let $N = \{ (q,v) \in \RR^{2n} | q \in M, v
\in (T_qM)^{\perp} \subset \RR^n \}$ be the normal bundle of $M$ in $\RR^n$. We
define a map $E$ that maps $N$ into the ambient space $\RR^n$ by
\begin{equation}
  E(q, v) = q + v.
\end{equation}
The point $q+v$ thus line in a normal line that is perpendicular to $M$ at
$p$. This leads to the definition of focal points:

\begin{defn}
  e \in \RR^n is a focal point of (M, q) with multiplicity \mu 
\end{defn}

\section{Manifolds in Euclidean Space: The Existence of Non-degenerate
  Functions}

\section{The Lefschetz Theorem on Hyperplane Sections}

\end{document}

### 2013-01-12 paper.tex
doing sec 6

@@
 
+\section{Manifolds in Euclidean Space: The Existence of Non-degenerate
+  Functions}
 Let $M$ be a smooth manifold of dimension $k$. By Whitney Embedding Theorem, we
-can embed $M$ into $\RR^n, n > k$. Let $N = \{ (q,v) \in \RR^{2n} | q \in M, v
-\in (T_qM)^{\perp} \subset \RR^n \}$ be the normal bundle of $M$ in $\RR^n$. We
-define a map $E$ that maps $N$ into the ambient space $\RR^n$ by
+can embed $M$ into $\RR^n, n > k$. Therefore, without loss of generality we may
+assume $M \subset \RR^n$. For each $p \in \RR^n$, define a smooth function $L_p
+: M \to \RR $ by
+\begin{equation}
+  L_p(q) = |q-p|^2.
+\end{equation}
+
+We want to find a $p \in \RR^n$ such that $L_p$ has no degenerate critical
+points in $M$. Let $q \in M$ and let $(u^1, .., u^k) \mapsto (x^1(u), ..,
+x^n(u))$ be a local coordinate at $q$. Then $q$ is a critical point if
+$\frac{\partial f}{\partial u^i}(q) = 0 \forall i = 1, .., k.$; that is,
+
+Let $N = \{ (q,v) \in \RR^{2n} | q \in M, v \in (T_qM)^{\perp} \subset \RR^n \}$
+be the normal bundle of $M$ in $\RR^n$. Then $N$ is a manifold of dimension
+$k+(n-k)=n$. We define a map $E$ that maps $N$ into the ambient space $\RR^n$ by
 \begin{equation}
@@
 \end{equation}
-The point $q+v$ thus line in a normal line that is perpendicular to $M$ at
-$p$. This leads to the definition of focal points:
+This is a differentiable map between two manifolds of dimension $n$. The point
+$q+v$ thus line in a normal line that is perpendicular to $M$ at $p$. This leads
+to the definition of focal points:
 
 \begin{defn}
-  e \in \RR^n is a focal point of (M, q) with multiplicity \mu 
+  $e \in \RR^n$ is a focal point of $(M, q)$ with multiplicity $\mu > 0$ if $e =
+  q+v$, where $(q, v) \in N$ and the Jacobian of $E$ at $(q, v)$ has nullity
+  $\mu > 0$. $e$ is called a focal point of $M$ if $e$ is a focal point of $(M,
+  q)$, $q \in M$.
 \end{defn}
 
-\section{Manifolds in Euclidean Space: The Existence of Non-degenerate
-  Functions}
+The focal points will play an important role in the construction of a kind
 

### 2013-01-12 paper.tex
finish ch6

@@
 \newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
+\newcommand{\vect}[1]{\vec{#1}}
 
@@
   Functions}
+
 Let $M$ be a smooth manifold of dimension $k$. By Whitney Embedding Theorem, we
@@
 \begin{equation}
-  L_p(q) = |q-p|^2.
+  L_p(q) = |q-p|^2 = (q-p) \cdot (q-p) = q\cdot q-2q \cdot p + p \cdot p
 \end{equation}
@@
 We want to find a $p \in \RR^n$ such that $L_p$ has no degenerate critical
-points in $M$. Let $q \in M$ and let $(u^1, .., u^k) \mapsto (x^1(u), ..,
-x^n(u))$ be a local coordinate at $q$. Then $q$ is a critical point if
-$\frac{\partial f}{\partial u^i}(q) = 0 \forall i = 1, .., k.$; that is,
+points in $M$. Denote $L_p$ as $f$. Let $q \in M$ and let $(u^1, .., u^k)
+\mapsto (x^1(u), .., x^n(u))$ be a local coordinate centered at $q$. Then $q$ is
+a critical point if $\frac{\partial f}{\partial u^i}(q) = 0$ for all $i = 1, ..,
+k.$; that is,
+\begin{equation}
+  \frac{\partial \vect{x}}{\partial u^i}(q) \cdot (q-p) = 0.
+\end{equation}
+It follows that $q \in M$ is a critical point of $L_p$ if and only if $p$ lies
+in a line perpendicular to $M$ at $q$. Differentiate again, and we get
+\begin{equation}
+  \frac{\partial^2 f}{\partial u^i \partial u^j}(q) = 
+  2\left(
+    \frac{\partial^2 \vect{x}}{\partial u^i \partial u^j}(q) \cdot (q-p) +
+    \frac{\partial \vect{x}}{\partial u^i}(q) \cdot \frac{\partial \vect{x}}{\partial u^j}(q)
+  \right)
+\end{equation}
+
+We get the following conclusions:
+
+$L_p$ is non-degenerate if and only if
+
+\begin{itemize}
+\item For each critical point $q$, $p$ lies in a line perpendicular to $M$ at
+  $q$.
+\item the matrix $\left(
+    \frac{\partial^2 \vect{x}}{\partial u^i \partial u^j}(q) \cdot (q-p) +
+    \frac{\partial \vect{x}}{\partial u^i}(q) \cdot \frac{\partial \vect{x}}{\partial u^j}(q)
+  \right)$
+  is non-singular.
+\end{itemize}
+
+Thus the main purpose of this section is to establish the existence of such $p
+\in \RR^n$.
+
+\subsection{Focal Points}
 
@@
 This is a differentiable map between two manifolds of dimension $n$. The point
-$q+v$ thus line in a normal line that is perpendicular to $M$ at $p$. This leads
+$q+v$ thus lies in a normal line that is perpendicular to $M$ at $p$. This leads
 to the definition of focal points:
@@
 
-The focal points will play an important role in the construction of a kind
+Next we fix a $\vect{q} \in M$ and a unit normal vector $\vect{v} \in \RR^n$ and
+study the focal points of $(M, q)$ along the line $\vect{l} =
+\vect{q}+t\vect{v}$. Before this, we first introduce the second the second
+fundamental form of a manifold in $\RR^n$:
+
+\begin{defn}
+  Let $\vect{q} \in M$ and let $\vect{v} \in (T_qM)^\perp$. The second
+  fundamental form in the direction of $\vect{v}$ is defined as the matrix
+
+  \begin{equation}
+    \left(
+      \vect{v} \cdot \vect{l}_{ij}
+    \right)
+  \end{equation}
+  where $\vect{l}_{ij} = \frac{\partial^2 \vect{x}}{\partial u^i \partial
+    u^j}(\vect{q})$.
+  The eigenvalues of the matrix is called the principal curvatures $K_1$, ..,
+  $K_k$ of $M$ at $\vect{q}$ in the normal direction $\vect{v}$.
+\end{defn}
+
+Now comes the key lemma in this section:
+
+\begin{lem}
+  The focal points of $(M, q)$ along $\vect{l}$  are precisely the points
+  $\vect{q}+K_i^{-1}\vect{v}$, where $1 \le i \le k$, $K_i \ne 0$. Thus there
+  are at most $k$ focal points of $(M,q)$ along $\vect{l}$, each being counted
+  with its proper multiplicity.
+\end{lem}
+
+\begin{proof}
+  First we are going to find a local coordinate of $N$ centered at $(q, v)$. Let
+  $\vect{w}_1(u^1, .., u^k)$, .., $\vect{w}_{n-k}(u^1, .., u^k)$ be orthonormal
+  vector fields in $N$. Then we have a local coordinate of $N$ at $(q, v)$
+  defined by
+  \begin{equation}
+    (u^1, .., u^k, t^1, .., t^{n-k}) \mapsto (\vect{x}(u),
+    \sum_{\alpha=1}^{n-k}t^{\alpha} \vect{w}_{\alpha}(u^1, .., u^k)) \in N
+  \end{equation}
+  Write $E: N \to \RR$ in the coordinate as $E(u, t) = \vect{e}(u, t) \in \RR^n$
+  and get
+  \begin{equation}
+    \vect{e}(u, t) = \vect{x}(u) + \sum_{\alpha=1}^{n-k}t^{\alpha} \vect{w}_{\alpha}(u^1, .., u^k))
+  \end{equation}
+  with partial derivatives
+  \begin{equation}
+    \left\{
+      \begin{array}{lcl}
+        \frac{\partial \vect{e}}{\partial u^i} & = &
+        \frac{\partial \vect{x}}{\partial u^i} + 
+        \sum_{\alpha} t^{\alpha}\frac{\vect{w}_{\alpha}}{\partial u^i}  \\
+        \frac{\partial \vect{e}}{\partial t^\beta} & = & \vect{w}_\beta
+      \end{array}
+    \right.
+  \end{equation}
+
+  Since the n-vectors $\frac{\partial \vect{x}}{\partial u^1}$, ..,
+  $\frac{\partial \vect{x}}{\partial u^k}$, $\vect{w}_1$, .., $\vect{w}_{n-k}$
+  form a basis of $T_q\RR^n$, the matrix
+  \begin{equation}
+    A = \left(
+      \begin{matrix}
+        \left(\frac{\partial \vect{x}}{\partial u^1}\right)^T \\
+        \vdots \\
+        \left(\frac{\partial \vect{x}}{\partial u^k}\right)^T \\
+        \left(\vect{w}_1\right)^T \\
+        \vdots \\
+        \left(\vect{w}_{n-k}\right)^T
+      \end{matrix}
+    \right)
+  \end{equation}
+  is non-singular (we represent a vector as a column matrix). Multiply $A$ with
+  the Jacobian $J$ of $E(u, t)$ and we get
+  \begin{equation}
+    \begin{aligned}
+      AJ &= 
+      \left(
+        \begin{matrix}
+          \left(\frac{\partial \vect{x}}{\partial u^1}\right)^T \\
+          \vdots \\
+          \left(\frac{\partial \vect{x}}{\partial u^k}\right)^T \\
+          \left(\vect{w}_1\right)^T \\
+            \vdots \\
+          \left(\vect{w}_{n-k}\right)^T
+        \end{matrix}
+      \right)
+      \left(
+        \begin{matrix}
+          \frac{\partial \vect{e}}{\partial u^1} &
+          \cdots &
+          \frac{\partial \vect{e}}{\partial u^k} &
+          \frac{\partial \vect{e}}{\partial t^1} &
+          \cdots &
+          \frac{\partial \vect{e}}{\partial t^{n-k}} &
+        \end{matrix}
+      \right) \\
+      &=
+      \left(
+        \begin{matrix}
+          \left( \frac{\partial \vect{x}}{\partial u^i} \cdot \frac{\partial
+              \vec{x}}{\partial u^j} + \sum_{\alpha}
+            t^{\alpha}\frac{\vec{w}_{\alpha}}{\partial u^i} \cdot \frac{\partial
+              \vect{x}}{\partial u^j} \right) & 0
+          \\
+          \sum_{\alpha} t^{\alpha}\frac{\vect{w}_{\alpha}}{\partial u^i} \cdot
+          \vect{w}_{\beta} & \id
+        \end{matrix}
+      \right)
+    \end{aligned}
+  \end{equation}
+
+  Since $J$ has the same rank of $AJ$, $J$ has the same nullity as the upper
+  left block of $AJ$. Using the identity
+  \begin{equation}
+    \begin{aligned}
+      0 &= \frac{\partial}{\partial u^i}\left(\vect{w}_{\alpha} \cdot
+        \frac{\partial
+          \vect{x}}{\partial u^j}\right) \\
+      &= t^{\alpha}\frac{\vect{w}_{\alpha}}{\partial u^i} \cdot \frac{\partial
+        \vect{x}}{\partial u^j} + \vect{w}_{\alpha} \cdot \frac{\partial^2
+        \vect{x}}{\partial u^i \partial u^j},
+    \end{aligned}
+  \end{equation}
+  we see that this upper left hand block is just the matrix 
+  \begin{equation}
+    \left( g_{ij} - \sum_{\alpha}t^{\alpha}\vect{w}_{\alpha} \cdot \vect{l}_{ij} \right)
+  \end{equation}
+
+  We choose the Riemman normal coordinate at $q$, so that $g_{ij}(q) =
+  \delta_{ij}$. Now, $\sum_{\alpha}t^{\alpha}\vect{w}_{\alpha} = t\vect{v}$. The
+  matrix
+  \begin{equation}
+    \label{eq:key}
+    \left(
+      \delta_{ij}-t\vect{v} \cdot  \vect{l}_{ij}
+    \right)
+  \end{equation}
+  is singular if and only if $\frac{1}{t} = K_i$. Furthermore, $\mu$ equals the
+  number of distinct $K_i$, each of which counted with its own
+  multiplicity. This proves the lemma.
+\end{proof}
+
+Suppose $\vect{p} = \vect{q}+t\vect{v}$. Then $\vect{q}$ is a critical point of
+$L_p$. Recall the criterion of $q$ being a non-degenerate critical point of
+$L_p$. The criterion is exactly Eq (\ref{eq:key}). We thus obtain the
+correspondence between the non-degeneracy of $L_p$ and the idea of focal points:
+
+\begin{cor}
+  The function $L_p$ is non-degenerate if and only if $p$ is not a focal point
+  of $M$. \qed
+\end{cor}
+
+$L_p$ is degenerate if and only if $p$ is a focal point, which is a critical
+value of a smooth map. By the following theorem of Sard, we see that there are
+infinitely many $p \in \RR^n$ such that $L_p$ is non-degenerate:
+
+\begin{thm}[Sard]
+  Let $f: M^m \to N^n$ be a smooth map between two smooth manifolds. Then the
+  critical values has measure 0 in $N^n$. \qed
+\end{thm}
+
+This established the existence of non-degenerate functions on $M$. As a result,
+the main theorem in this report is proved:
+
+\begin{thm}
+  A differentiable manifold has the homotopy type of a CW-complex.\qed
+\end{thm}
+
+The preceding corollary can be sharpened as follows. Let $k \ge 0$ be an integer
+and let $K \subset M$ be a compact set.
+
+\begin{cor}
+  Any bounded smooth function $f: M \to \RR$ can be uniformly approximated by a
+  smooth function $g$ which has no degenerate critical points. Furthermore $g$
+  can be chosen so that the i-th derivatives of $g$ on the compact set $K$
+  uniformly approximate the corresponding derivatives of $f$, for $i \le k$.
+\end{cor}
+
+\begin{proof}
+  Choose some embedding $h:M \to \RR^n$ of $M$ as a bounded subset of some
+  euclidean space so that the first coordinate $h_1$ is exactly
+  $f$. \footnote{By Whitney embedding theorem, there is an embedding $\phi : M
+    \in R^n$. Compose each coordinate of $\phi$ with $arctan$, we get a bounded
+    embedding, since $\psi = (\tan^{-1} \circ \phi^1, .., \tan^{-1} \circ
+    \phi^n)$ is one-to-one and the differential map is injective. Let $h = (f,
+    \tan^{-1}\phi)$. Then $h$ is an embedding from $M$ into $\RR^{n+1}$ such
+    that $h_1 = f$.} Let c be a large number. Choose a point
+  \begin{equation}
+    p = (-c+\epsilon_1, \epsilon_2, .., \epsilon_n)
+  \end{equation}
+  close to $(-c, 0, .., 0) \in \RR^n$ such that the function $L_p: M \to \RR$ is
+  non-degenerate. Define
+  \begin{equation}
+    g(x) = \frac{L_p(x)-c^2}{2c}
+  \end{equation}
+  A short computation gives
+  \begin{equation}
+    \begin{aligned}
+      g(x) &= \frac{\sum_i h_i^2(x)-h_i(x)p_i+p_i^2-c^2}{2c} \\
+           &= f(x) + \frac{\sum_i h_i^2(x)-\sum_i h_i(x)\epsilon_i+\sum_i \epsilon_i^2}{2c}-\epsilon_1.
+    \end{aligned}
+  \end{equation}
+  Since $K$ is compact and each $h_i$ is continuous and bounded, it's easy to
+  see that $g(x)$ approximates $f(x)$ uniformly by choosing $c$ large enough and
+  $\epsilon_i$ small enough. 
+\end{proof}
+
+The preceding theory can also be used to describe the index of the function
+$L_p$ at a critical point:
+
+\begin{lem}[Index theorem for $L_p$]
+  The index of $L_p$ at a non-degenerate critical point $q \in M$ is equal to
+  the number of focal points of (M, q) which lie on the segment from $q$ to $p$;
+  each focal point being counted with its multiplicity.
+\end{lem}
+
+\begin{proof}
+  The index of the matrix 
+  \begin{equation}
+    \left( \frac{\partial^2 L_p}{\partial u^i \partial
+        u^j}(q) \right) = 2(g_{ij}-t\vect{v} \cdot \vect{l}_{ij})
+  \end{equation}
+  equals the number of negative eigenvalues counting with multiplicity. Recall
+  that we can choose the normal coordinate such that $(g_{ij})$ is
+  identity. Then$\left( \frac{\partial^2 L_p}{\partial u^i \partial u^j}(q)
+  \right)$ has a negative eigenvalue if and only if $1-K_it < 0$ for some
+  principal curvatures $K_i$. Thus $K_i > \frac{1{t}$. Recall that the focal
+    points that lies on the line from $q$ through $p$ are of the form
+    $\vect{q}+K_i^{-1}\vect{v}$. Therefore the correspondece established.
+
+\end{proof}
 

### 2013-01-15 paper.tex
finish ch6
oh yeah

@@
-\documentclass[12pt]{article}
+% \documentclass[12pt]{article}
+\documentclass[a4paper,11pt,reqno]{amsart}
 
@@
 \newtheorem{defn}[thm]{Definition}
+\newtheorem{asser}[thm]{Assertion}
+\newtheorem{rmk}[thm]{Remark}
 
@@
 is equivalent to $\frac{\partial f}{\partial x^i} (p) = 0$ for all $i = 1,
-.. ,k$ and any local coordinate $(x^1, .., x^k)$, since the map $df_p$ in local
-coordinate is a row matrix with a non-empty kernel.
+.. ,k$ and any local coordinate system $(x^1, .., x^k)$, since the map $df_p$ in
+local coordinates is a row matrix with a non-empty kernel.
 
 \begin{defn}
-  (Non-degenerate critical point) Let $p \in M$ and let $(x^1, .., x^k)$ be a
-  local coordinate at $p$. $p$ is called a non-degenerate critical point of $f$
-  if
+  Let $p \in M$ and let $(x^1, .., x^k)$ be a local coordinate system centered
+  at $p$. $p$ is called a non-degenerate critical point of $f$ if
   \begin{equation}
@@
 
+The non-degeneracy of critical points also has an intrinsic meaning. Let $p$ be
+a critical point. We define a symmetric bilinear form $f_{**}$ on $T_PM$, called
+the \emph{Hessian} of $f$ at $p$. If $v, w \in T_pM$, then $v$ and $w$ have
+extensions $\tilde{v}, \tilde{w}$. Define $f_{**}(v, w) =
+\tilde{v}_p((\tilde{w})f)$. We must show that this is symmetric and
+well-defined.$f_{**}$ is symmetric, since $\tilde{v}_p((\tilde{w})f) -
+\tilde{w}_p((\tilde{v})f) = [\tilde{v}, \tilde{w}_p](f) = 0$\footnote{The last
+  equality holds because $p$ is a critical point of $f$.} Therefore $f_{**}(v,
+w) = v((\tilde{w})f) = w((\tilde{v})f)$. From both expressions of $f_{**}$ we
+see that the definition is independent of the extensions of $v$ and $w$.
+
+If $(x^1, .., x^n)$ is a local coordinate system, then the bilinear form
+$f_{**}$ can be expressed as a symmetric matrix $\left(\frac{\partial^2
+    f}{\partial x^i \partial x^j}(p)\right)$. Thus $p$ is a non-degenerate
+critical point if the Hessian of $f$ at $p$ is a non-degenerate symmetric form.
+
+Let $p$ be a critical point. We define the \emph{index of $f$ at $p$} as the
+maximal dimension of subspaces in which $f_{**}$ is negative definite. The
+\emph{nullity} is the subspace $V$ of $T_pM$ such that $f_{**}(V,w) = 0$ for all
+$w \in T_pM$. The lemma of Morse shows that the behavior of $f$ at $p$ can be
+completely described by this index. Before proving this, there is a small lemma:
+
+\begin{lem}
+  Let $f$ be a smooth function in a convex neighborhood $V$ of $0$ in $\RR^n$,
+  with $f(0) = 0$. Then
+  \begin{equation}
+    f(x_1, .., x_n) = \sum_{i=1}^{n} x_ig_i(x_1, .., x_n)
+  \end{equation}
+  for some smooth $g_i$ defined in $V$, with $g_i(0) = \frac{\partial
+    f}{\partial x_i}(0)$.
+\end{lem}
+
+\begin{proof}
+  \begin{equation}
+    \begin{aligned}
+      f(x_1, .., x_n) &= \int_0^1 \frac{d f(tx_1, .., tx_n)}{dt} dt \\
+                     &= \int_0^1 \sum_{i=1}^{n} x_i\frac{\partial f}{\partial
+                       x_i}(tx_i) dt
+    \end{aligned}
+  \end{equation}
+  Set $g_i = \int_0^1 \sum_{i=1}^{n} \frac{\partial f}{\partial x_i}(tx_i) dt$.
+\end{proof}
+
+\begin{lem}[Lemma of Morse]
+  Let $p$ be a non-degenerate critical point for $f$. Then there is a local
+  coordinate system $(y^1, .., y^n)$ in a neighborhood $U$ of $p$ with $y^i(p) =
+  0$ and for all $i$ and such that the identity
+  \begin{equation}
+    f = f(p) - (y^1)^2 - .. - (y^\lambda)^2 + (y^{\lambda+1})^2 + .. + (y^n)^2
+  \end{equation}
+  where $\lambda$ is the index of $f$ at $p$.
+\end{lem}
+
+\begin{proof}
+  Suppose such a local coordinate system exists. We prove that $\lambda$ must be
+  the index of $f$ at $p$. If
+  \begin{equation}
+        f(q) = f(p) - (y^1(q))^2 - .. - (y^\lambda(q))^2 + (y^{\lambda+1}(q))^2 + .. + (y^n(q))^2,
+  \end{equation}
+  then
+  \begin{equation}
+    \frac{\partial^2 f}{\partial y^i \partial y^j} = 
+    \begin{cases}
+      -2 & i = j \le \lambda, \\
+      2  & i = j > \lambda, \\
+      0  & otherwise,
+    \end{cases}
+  \end{equation}
+  which shows that $\lambda$ is the index of $f$ at $p$.
+
+  We now show that such a local coordinate system exists.
+
+  Let $(x^1, .., x^n)$ be a local coordinate system in a neighborhood $U$ of
+  $p$, such that $x^i(p) = 0$ for all $i$. We may also suppose that $f(p) = 0$.
+  By the previous lemma we can write
+  \begin{equation}
+    f(x_1, .., x_n) = \sum_j x_jg_j(x_1, .., x_n)
+  \end{equation}
+  Since $p$ is a critical point, 
+  \begin{equation}
+    0 = \frac{\partial f}{\partial x^j}(0) = g_j(0).
+  \end{equation}
+
+  Applying the lemma to $g_j$, we have
+  \begin{equation}
+    g_j(x) = \sum_i x_ih_{ij}(x_1, .., x_n).
+  \end{equation}
+  It follows that
+  \begin{equation}
+    f(x_1, .., x_n) = \sum_{i,j} x^ix^jh_{ij}(x_1, .., x_n).
+  \end{equation}
+
+  We may assume $h_{ij}$ is symmetric, since we can write $\bar{h}_{ij} =
+  \frac{1}{2}(h_{ij}+h_{ji})$ and get $f = \sum_{i,j}
+  x^ix^j\bar{h}_{ij}$. Moreover, $\bar{h}_{i,j}(0) = \frac{1}{2}\frac{\partial^2
+    f}{\partial x^i \partial x^j}(0)$, so it is non-singular.
+
+  By induction, we proceed to find the local coordinate system to express $f$ in
+  the desired form. Suppose by induction we have coordinates $u_1, .., u_n$ in a
+  neighborhood $U$ of $p$ such that
+  \begin{equation}
+    f = \pm (u_1)^2 \pm .. \pm (u_{r-1})^2 + \sum_{i, j \ge r} u_iu_jH_{ij}(u_1,
+    .., u_n),
+  \end{equation}
+  where $H_{ij}$ is symmetric and non-singular at $0$. After a linear
+  change\footnote{If some of the diagonal elements is nonzero, say $H_{qq}$, we
+    swap the two coordinates $u_r$ and $u_q$. If all diagonal elements are
+    zeros, then we choose $k > r$ such that $\frac{\partial^2 f}{\partial
+      u^r \partial u^{k}} \ne 0$. Define new coordinates $(w^1, .., w^n) = (u^1,
+    .., u^{r-1}, \frac{u^r+u^k}{2}, u^{r+1}, .., u^{k-1}, \frac{u^r-u^k}{2},
+    u^{k+1}, .., u^n)$. Then $\frac{\partial^2 f}{\partial w^r \partial w^r} =
+    2\frac{\partial^2 f}{\partial u^r \partial u^k} \ne 0$, as desired.} in the
+  last $n-r+1$ coordinates, we may assume that $H_{rr}(0) \ne 0$.Put $g(u_1, ..,
+  u_n) = \sqrt{|{H_{rr}}|}$. Then there is a smaller neighborhood $U_2 \subset
+  U_1$ of $p$ such that $g \ne 0$. A short calculation shows:
+
+  \begin{equation}
+    \begin{aligned}
+      \sum_{i,j\ge r}u_iu_jH_{ij} 
+      &= (u_r)^2H_{rr} + 2\sum_{i>r}u_iu_rH_{ir}+\sum_{i,j>r}u_iu_jH_{ij} \\
+      &= \pm g(u_r+\sum_{i>r}\frac{u_iH_{ir}}{H_{rr}})^2+\sum_{i,j>r}u_iu_jH_{ij}',
+    \end{aligned}
+  \end{equation}
+  where
+  \begin{equation}
+    H_{ij}' = H_{ij}-\frac{H_iH_j}{H_{rr}}
+  \end{equation}
+  is symmetric.
+
+  Define new local coordinates
+  $v_1$, .., $v_n$ by
+  \begin{equation}
+    v_i = 
+    \begin{cases}
+      u_i & i \ne r \\
+      g(u_1, .., u_n)\left[u_r+\sum_{i>r}\frac{u_iH_{ir}}{H_{rr}}\right] & i = r
+    \end{cases}
+  \end{equation}
+
+  By induction, the proof is complete.
+
+\end{proof}
+
+\begin{defn}
+  A 1-parameter group of diffeomorphisms of a manifold $M$ is a smooth map
+  \begin{equation}
+    \phi : \RR \times M \to M
+  \end{equation}
+  such that
+  \begin{itemize}
+  \item for each $t \in \RR$ the map $\phi_t : M \to M$ defined by $\phi_t(q) =
+    \phi(t, q)$ is a diffeomorphism of $M$ onto itself, and that
+  \item for all $t,s \in \RR$, $\phi_{t+s} = \phi_t \circ \phi_s$.
+  \end{itemize}
+\end{defn}
+
+\begin{lem}
+  A smooth vector field on $M$ which vanishes outside of a compact set $K
+  \subset M$ generates a unique 1-parameter group of diffeomorphisms on $M$.
+\end{lem}
+
+\begin{proof}
+  Let $p \in M$. Then there exists a neighborhood $U$ of $p$ and $\epsilon > 0$
+  such that the local flow $\phi : (-\epsilon, \epsilon)\times U \to M$ exists
+  and is unique and the dependence on initial values is smooth. Since $K$ is
+  compact, it can be covered by a finite number of $U$. Let $\epsilon_0$ be the
+  smallest $\epsilon$ and set $\phi_t(q) = q$ for all $q \notin K$. Then the
+  flow $\phi: (-\epsilon_0, \epsilon_0)\times M \to M$ exists and is unique. If
+  $|s|,|t,|s+t| < \epsilon_0$ and set $f(t) = \phi_t(q)$. Then $\frac{df}{dt} =
+  X_{f(t)}$ and $f(0) = \phi_s(q)$. Then $f(t) = \phi_{t+s}(q)$ by
+  uniqueness. Thus $\phi_{t+s} = \phi_t \circ \phi_s$.
+
+  We can extend the time domain from $(-\epsilon_0, \epsilon_0)$ to $\RR$ by
+  define
+  \begin{equation}
+    \phi_t = \phi_{\frac{\epsilon_0}{2}} \circ \phi_{\frac{\epsilon_0}{2}} \circ
+    .. \circ \phi_{\frac{\epsilon_0}{2}} \circ \phi_r,
+  \end{equation}
+  where $t = k\frac{\epsilon_0}{2}+ r$ and $|r| \le \frac{\epsilon_0}{2}$.
+\end{proof}
+
 \section{Homotopy Type in Terms of Critical Values}
+
+Let $M$ be a smooth manifold and let $f: M \to \RR$ be a smooth function without
+degenerate critical points. First we define
+\begin{equation}
+  M^a = f^{-1}(-\infty, a] = \{ p \in M | f(p) \le a \}.
+\end{equation}
+
+Then we investigate the ``topological difference'' between $M^a$ and $M^b$,
+where $a < b$. The first case is simpler, namely there is no critical point in
+$f^{-1}[a,b]$:
+
+\begin{thm}
+  Suppose $f^{-1}[a,b]$ is compact and contains no critical points of $f$. Then
+  $M^a$ is diffeomorphic to $M^b$. Furthermore, $M^a$ is a deformation retract
+  of $M^b$, so that the inclusion map $\iota : M^a \to M^b$ is a homotopy
+  equivalence.
+\end{thm}
+
+\begin{proof}
+  Intuitively, we try to ``squeeze'' $M^b$ into $M^a$ in the direction of the
+  gradient of $f$. Choose a Riemannian metric on $M$ and denote the inner
+  product as $\langle X, Y \rangle$. The \emph{gradient} of $f$ is characterized
+  by the identity\footnote{In fact, it is uniquely defined. To see this, choose
+    local coordinates $u^1$, .., $u^n$ and put $X = \frac{\partial}{\partial
+      u^i}$ into the identity. Write $grad \: f = f^j\frac{\partial}{\partial
+      u^j}$. Then identity becomes $g_{ij}\frac{\partial}{\partial u^j} =
+    \frac{\partial f}{\partial u^i}$. Taking inverse of the matrix $(g_{ij})$,
+    we get $a^j = g^{ji}\frac{\partial f}{\partial u^i}$.}
+  \begin{equation}
+    \langle X, grad \: f\rangle = X(f)
+  \end{equation}
+
+  Let $\rho : M \to \RR$ be a smooth function which is equal to $1/\langle grad
+  \: f, grad \: f \rangle$ throughout the compact set
+  $f^{-1}[a,b]$\footnote{$grad \: f \ne 0$ in $f^{-1}[a,b]$; otherwise there is
+    a critical point. It is easy to check this in terms of normal coordinates.}
+  , and which vanishes outside of a compact neighborhood of this set. Then the
+  vector field 
+  \begin{equation}
+    X = \rho (grad \: f)
+  \end{equation}
+  satisfies the condition in the last lemma of the previous section. Hence $X$
+  generates a 1-parameter group of diffeomorphisms
+  \begin{equation}
+    \phi_t : M \to M.
+  \end{equation}
+
+  For fixed $q \in M$ consider the function $t \mapsto f(\phi_t(q))$. Then If
+  $\phi_t(q) \in f^{-1}[a,b]$, then
+  \begin{equation}
+    \frac{d f(\phi_t(q))}{dt} = X_{\phi_t q}(f) = +1
+  \end{equation}
+  Hence the correspondence $t \mapsto f(\phi_t(q))$ is linear as long as
+  $f(\phi_t(q)) \in [a,b]$. It follows that $f(\phi_{t}(q)) = t + f(q)$ in a
+  small neighborhood of $0 \in \RR$, where $q \in f^{-1}[a,b]$.
+
+  Consider the diffeomorphism $\phi_{b-a} : M \to M$. By above it's clear
+  that $\phi_{b-a}$ maps $M^a$ diffeomorphically onto $M^b$. This prove the
+  first part of the theorem.
+
+  Now we construct a 1-parameter family of maps by
+  \begin{equation}
+    r_t(q) =
+    \begin{cases}
+      q & if f(q) \le a \\
+      \phi_{t(a-f(q))}(q) & if a \le f(q) \le b.
+    \end{cases}
+  \end{equation}
+
+  Then $r : [0,1] \times M^b \to M^a$ is a homotopy between identity of $M^a$
+  and the deformation retract from $M^b$ to $M^a$. This completes the proof.
+\end{proof}
+
+The case when $f^{-1}[a,b]$ contains a critical point of $f$ is the essential
+part of the Morse theory. It can be shown that $M^b$ is just $M^a$ with a number
+of cells attached.
+
+\begin{thm}
+  Let $f: M \to \RR$ be a smooth function and let $p$ be a non-degenerate
+  critical point with index $\lambda$. Setting $f(p) = c$, suppose that $p$ is
+  the only critical point in $f^{-1}[c-\epsilon, c+\epsilon]$, for some
+  $\epsilon > 0$. Then for all $\epsilon$ sufficiently small, the set
+  $M^{c-\epsilon}$ has the same homotopy type of $M^{c+\epsilon}$ with a
+  $\lambda$-cell attached.
+\end{thm}
+
+The idea of the proof is to define a new smooth function $F: M \to \RR$ such
+that inside a small neighborhood $H$ of $p$, $F < f$, and that $F = f$ outside
+$H$. So $F^{-1}[-\infty, c-\epsilon] = M^{c-\epsilon} \cup H$ and
+$F^{-1}[-\infty,c+\epsilon] = M^{c+\epsilon}$. If $F^{-1}[c-\epsilon,
+c+\epsilon]$ has no critical point and is compact, then $M^{c-\epsilon} \cup H$
+is a deformation retract of $M^{c+\epsilon}$ by the preceding theorem. If $H$
+can be deformed into a $\lambda$-cell in it, the theorem is proved.
+
+By the idea above, we divide the proof of the theorem into the following
+steps.
+
+Choose a coordinate system $u^1$, .., $u^n$ in a neighborhood $U$ of $p$ so that
+the identity
+\begin{equation}
+  f = c - (u^1)^2 - .. - (u^{\lambda})^2 + (u^{\lambda+1})^2 + .. + (u^{n})^2
+\end{equation}
+holds throughout $U$ (Morse lemma). Then at $p$ we have $u^i(p) = 0$, $i = 1,
+.., n$.
+
+Choose $\epsilon > 0$ sufficiently small so that
+\begin{itemize}
+\item The region $f^{-1}[c-\epsilon,c+\epsilon]$ is compact and contains no
+  critical points other than p.
+\item The diffeomorphic image of $U$ in $\RR^n$ contains the closed ball
+  $\{\sum_i (u^i)^2 \le 2\epsilon\}$.
+\end{itemize}
+
+Then $U$ contains a $\lambda$-cell, namely the inverse image of
+$\{(u^1)^2+..+(u^{\lambda})^2 \le \epsilon, u^{\lambda+1}=..=u^{n} = 0\}$. Note
+that $e^\lambda \cap M^{c-\epsilon}$ is exactly $\{f = c- \epsilon\} =
+\{(u^1)^2+..+(u^\lambda)^2 = \epsilon \}$. So that the $\lambda$-cell is really
+attached to $M^{c-\epsilon}$.
+
+Next we construct a new smooth function $F : M \to \RR$ as follows. Let $\mu
+:\RR \to \RR$ be a smooth function satisfying the conditions
+\begin{equation}
+  \begin{cases}
+    \mu(0) > \epsilon \\
+    \mu(r) = 0 \: \forall r \ge 2\epsilon \\
+    -1 < \mu'(r) \le 0 \: \forall r.
+  \end{cases}
+\end{equation}
+
+For example, we can define $\mu$ as follows. Let $\mu = \epsilon'
+\frac{\int_x^{2\epsilon} \alpha(t)\alpha(2\epsilon-t)}dt{\int_0^{2\epsilon}
+  \alpha(t)\alpha(2\epsilon-t)}dt$, where $2\epsilon > \epsilon' > \epsilon$ and
+\begin{equation}
+  \alpha(x) =
+  \begin{cases}
+    0 & x \le 0 \\
+    e^{-1/x} & x > 0
+  \end{cases}
+\end{equation}
+is smooth. Then $0 \ge \mu'(r) > -\frac{\epsilon'}{2\epsilon} > -1$.
+
+Now let F coincides with f outside of the coordinate neighborhood $U$, and let
+\begin{equation}
+  F = f -\mu((u^1)^2+..+(u^{\lambda})^2 + 2(u^{\lambda+1})^2+..+(u^{n})^2)
+\end{equation}
+within $U$. It is easily verified that $F$ is a well-defined smooth function
+throughout $M$.
+
+It is convenient to write $\xi = (u^1)^2+..+(u^{\lambda})^2$ and $\eta =
+(u^{\lambda+1})^2+..+(u^{n})^2$.
+
+\begin{asser}
+  The region $F^{-1}(-\infty, c+\epsilon]$ coincides with the region $M^{c+\epsilon}$.
+\end{asser}
+
+\begin{proof}
+  Let $A = f^{-1}[-\infty, c+\epsilon]$, and let $B = F^{-1}[-\infty,
+  c+\epsilon]$. If $q \in A$, then $F(q) \le f(q) \le c+\epsilon$ and so $q \in
+  B$. To prove the converse, let $q \in B$. If $q \in \{ \xi + 2\eta \le
+  2\epsilon \}$, then $f(q) = c - \xi + \eta \le c+ \frac{1}{2}\xi + \eta \le
+  c+\epsilon$. If $q \notin \{ \xi + 2\eta \le 2\epsilon \}$, then $f(q) =
+  F(q) \le c+\epsilon$. In both cases, $q \in A$.
+\end{proof}
+
+\begin{asser}
+  The critical points of $F$ are the same as those of $f$.
+\end{asser}
+
+\begin{proof}
+  \begin{equation}
+    \nonumber
+    \begin{aligned}
+      F &= c - \xi + \eta - \mu(\xi+2\eta) \\
+      \frac{\partial F}{\partial \xi} &= -1 - \mu'(\xi+2\eta) < 0 \\
+      \frac{\partial F}{\partial \eta} &= 1 - 2\mu'(\xi+2\eta) ge 1 \\
+      dF &= \frac{\partial F}{\partial \xi}d\xi+\frac{\partial F}{\partial
+        \eta}d\eta
+    \end{aligned}
+  \end{equation}
+  Since the 1-forms $d\xi$ and $d\eta$ are simultaneously 0 only when both
+  $\xi$ and $\eta$ equal 0, it follows that $F$ has no critical point in $U$
+  other than $p$.
+\end{proof}
+
+Now, since $F \le f$, if $q \in F^{-1}[c-\epsilon, c+\epsilon]$, then
+$c-\epsilon \le f(q)$. But $q \in F^{-1}(-\infty, c+\epsilon] = f^{-1}(-\infty,
+c+\epsilon]$, $f(q) \le c+ \epsilon$. Therefore $q \in f^{-1}(-\infty,
+c+\epsilon]$. This proves that $F^{-1}[c-\epsilon, c+\epsilon] \subset
+f^{-1}[c-\epsilon, c+\epsilon]$. Being a closed subset of a compact set in a
+locally compact Hausdorff space, $F^{-1}[c-\epsilon, c+\epsilon]$ is compact.
+Note that $F(p) = c- \mu(0) \le c-\epsilon$. $p \notin F^{-1}[c-\epsilon,
+c+\epsilon]$. Together with the preceding theorem we get
+
+\begin{asser}
+  $F^{-1}(-\infty, c-\epsilon]$ is a deformation retract of $F^{-1}[-\infty,
+  c+\epsilon]$. \qed
+\end{asser}
+
+Write $F^{-1}(-\infty, c-\epsilon]$ as $M^{c-\epsilon}\cup H$, where $H$ is the
+closure of $F^{-1}(-\infty, c-\epsilon] - M^{c-\epsilon}$. In fact, $H = \{
+\epsilon-\mu(\xi+2\eta) \le \xi-\eta \le \epsilon \}$. Define
+\begin{equation}
+  e^\lambda = \{ q | \xi(q) \le \epsilon, \eta(q) = 0\}
+\end{equation}
+Then $e^\lambda \subset H$. For, if $q \in e^\lambda$, then $f(q) >
+c-\epsilon$. Thus $q \notin M^{c-\epsilon}$. Also, since $\frac{\partial
+  F}{\partial \xi} < 0$, $F(q) < F(p) < c-\epsilon$. Thus $q \in F^{-1}(-\infty,
+c-\epsilon]$.
+
+\begin{asser}
+  $M^{c-\epsilon} \cup e^\lambda$ is a deformation retract of
+  $M^{c-\epsilon}\cup H$.
+\end{asser}
+
+\begin{proof}
+  We operate on the diffeomorphic image on $\RR^n$. In the $\xi-\eta$ plane, $H$
+  is the region $F \ge c-\epsilon$ minus the region $f \ge c-\epsilon$.
+
+  Denote the homotopy between the retraction and identity by $r_t : [0,1]\times
+  (M^{c-\epsilon}\cup H) \to M^{c-\epsilon} \cup e^\lambda$.
+
+  Decompose $H$ into 2 regions: (1) $\xi \le \epsilon$ and (2) $\epsilon \le \xi
+  \le \eta + \epsilon$.
+
+  In region (1), we simply project $H$ into $e^\lambda$. The homotopy is thus
+  given by 
+  \begin{equation}
+    r_t: (t, (u^1,..,u^n)) \mapsto (u^1, .., u^\lambda, tu^{\lambda+1}, .., tu^n).
+  \end{equation}
+
+  We check that the homotopy lies entirely in $H =
+  \{\epsilon-\mu(\xi+2\eta) \le \xi-\eta \le \epsilon \}$. It does,
+  indeed, since $\epsilon \ge \xi > \xi-t^2\eta > \xi-\eta \ge
+  \epsilon-\mu(\xi+2\eta) \ge \epsilon-\mu(\xi+2t\eta)$.
+
+  In region (2), we project this part into $M^{c-\epsilon}$, in the
+  $\eta$-direction as the in case (1). Let the following denote the projection:
+  \begin{equation}
+    (u^1, .., u^n) \mapsto
+    (u^1, .., u^\lambda, cu^{\lambda+1}, .., cu^n) \in M^{c-\epsilon}
+  \end{equation}
+
+  Then it's easy to calculate $c =
+  (\frac{\xi-\epsilon}{\eta})^{\frac{1}{2}}$. Then the homotopy is simply the
+  line along the projection:
+  \begin{equation}
+    r_t: (t, (u^1,..,u^n)) \mapsto
+    (u^1, .., u^\lambda, s_tu^{\lambda+1}, .., s_tu^n),
+  \end{equation}
+  where
+  \begin{equation}
+    s_t = t + (1-t)c.
+  \end{equation}
+
+  Again we check that the homotopy lies entirely in $H$. This is true, since
+  $s_t \in [0,1]$. More precisely, $\xi-s_t^2\eta \ge \xi-\eta \ge
+  \epsilon-\mu$.
+
+  Since $s_t$ is continuous and it is compatible with the case (1) when $\xi =
+  \epsilon$, $r_t$ is well-defined and continuous on the union.
+
+  It remains to define $r_t$ on $M^{c-\epsilon}$. We simply define it as the
+  identity map. Note that this definition is compatible with that of case (2),
+  since on $\xi-\eta=\epsilon$, $s_t = 1$.
+
+  The assertion follows.
+\end{proof}
+
+As the last assertion is proved, so is the theorem.
+
+\begin{rmk}
+  More generally suppose that there are $k$ non-degenerate critical points
+  $p_1$, .., $p_k$ with indices $\lambda_1$, .., $\lambda_k$ in
+  $f^{-1}(c)$. Then a similar proof shows that $M^{c+\epsilon}$ has the homotopy
+  type of $M^{c-\epsilon}\cup e^{\lambda_1}\cup .. \cup e^{\lambda_k}$.
+\end{rmk}
+
+\begin{lem}[Whitehead]
+  Let $\phi_0$ and $\phi_1$ be homotopic maps from the sphere $\dot{e}^\lambda$
+  to $X$. Then the identity map of $X$ extends to a homotopy equivalence
+  \begin{equation}
+    k: X \cup_{\phi_0} e^\lambda \to X \cup_{\phi_1} e^\lambda
+  \end{equation}
+\end{lem}
 
@@
 points in $M$. Denote $L_p$ as $f$. Let $q \in M$ and let $(u^1, .., u^k)
-\mapsto (x^1(u), .., x^n(u))$ be a local coordinate centered at $q$. Then $q$ is
+\mapsto (x^1(u), .., x^n(u))$ be a local coordinate system centered at $q$. Then $q$ is
 a critical point if $\frac{\partial f}{\partial u^i}(q) = 0$ for all $i = 1, ..,
@@
 \begin{defn}
-  Let $\vect{q} \in M$ and let $\vect{v} \in (T_qM)^\perp$. The second
-  fundamental form in the direction of $\vect{v}$ is defined as the matrix
+  Let $\vect{q} \in M$ and let $\vect{v} \in (T_qM)^\perp$, $|\vect{v}| =
+  1$. When $g_{ij} = \delta_{ij}$, the second fundamental form\footnote{The more
+    general definition is $-(\nabla \tilde{v})^T$, which is a linear
+    transformation on $T_qM$. If $(u^1, .., u^k)$ is a normal coordinate system,
+    the matrix of the second fundamental from is given by $(-\nabla^T
+    \tilde{v})_{ij} = -\frac{\partial \tilde{v}}{\partial u^j} \cdot
+    \frac{\partial x}{\partial u^i} = v \cdot \frac{\partial^2 x}{\partial
+      u^i \partial u^j}$.} in the direction of $\vect{v}$ is defined as the
+  matrix
 
@@
 \begin{proof}
-  First we are going to find a local coordinate of $N$ centered at $(q, v)$. Let
-  $\vect{w}_1(u^1, .., u^k)$, .., $\vect{w}_{n-k}(u^1, .., u^k)$ be orthonormal
-  vector fields in $N$. Then we have a local coordinate of $N$ at $(q, v)$
-  defined by
+  First we are going to find a local coordinate system of $N$ centered at $(q,
+  v)$. Let $\vect{w}_1(u^1, .., u^k)$, .., $\vect{w}_{n-k}(u^1, .., u^k)$ be
+  orthonormal vector fields in $N$. Then we have a local coordinate system of
+  $N$ at $(q, v)$ defined by
   \begin{equation}
@@
   \end{equation}
-  Write $E: N \to \RR$ in the coordinate as $E(u, t) = \vect{e}(u, t) \in \RR^n$
-  and get
+  Write $E: N \to \RR$ in the coordinates as $E(u, t) = \vect{e}(u, t) \in
+  \RR^n$ and get
   \begin{equation}
@@
 
-  We choose the Riemman normal coordinate at $q$, so that $g_{ij}(q) =
+  We choose the Riemman normal coordinates at $q$, so that $g_{ij}(q) =
   \delta_{ij}$. Now, $\sum_{\alpha}t^{\alpha}\vect{w}_{\alpha} = t\vect{v}$. The
@@
   \end{equation}
-  equals the number of negative eigenvalues counting with multiplicity. Recall
-  that we can choose the normal coordinate such that $(g_{ij})$ is
+  equals the number of negative eigenvalues counted with multiplicity. Recall
+  that we can choose the normal coordinates such that $(g_{ij})$ is
   identity. Then$\left( \frac{\partial^2 L_p}{\partial u^i \partial u^j}(q)
   \right)$ has a negative eigenvalue if and only if $1-K_it < 0$ for some
-  principal curvatures $K_i$. Thus $K_i > \frac{1{t}$. Recall that the focal
+  principal curvatures $K_i$. Thus $K_i > \frac{1}{t}$. Recall that the focal
   points that lies on the line from $q$ through $p$ are of the form
-    $\vect{q}+K_i^{-1}\vect{v}$. Therefore the correspondece established.
+  $\vect{q}+K_i^{-1}\vect{v}$. Therefore the correspondence established.
 
@@
 
+As an application of the previous results,
+
 \end{document}

### 2013-01-15 paper.tex
start working on the last section

@@
 \newcommand{\ZZ}{\mathbb{Z}}      % for Integers
+\newcommand{\CC}{\mathbb{C}}
 \newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
@@
 
-As an application of the previous results,
+As an application of the previous results, we will prove the Lefschetz theorem
+on hyperplane sections in this section. Before the development, we should show
+that every complex analytic manifold can be viewed as a CW-complex:
+
+\begin{thm}
+  A complex manifold analytic manifold $M$ of complex dimension $k$,
+  bianalytically embedded as a closed subset of $\CC^n$ has the homotopy type of
+  a $k$-dimensional CW-complex.
+\end{thm}
+
+The proof will be broken up into several steps. First we consider a quadratic
+form in $k$ complex variables
+\begin{equation}
+  Q(z^1, .., z^k) = \sum b_{hj}z^hz^j.
+\end{equation}
+
+If we substitute $x^h+iy^h$ for $z^h$ and take the real part of $Q$, we obtain a
+real quadratic form in $x^1, .., x^k, y^1, .., y^k$:
+
+\begin{equation}
+  Q'(x^1, .., x^k, y^1, .., y^k) = Re\{\sum b_{hj}z^hz^j\}.
+\end{equation}
+
+\begin{asser}
+  If $e$ is an eigenvalue of $Q'$ with multiplicity $\mu$, then $-e$ is also an
+  eigenvalue with the same multiplicity $\mu$.
+\end{asser}
+
+\begin{proof}
+  First we note that $Q(iz^1, .., iz^k) = -Q(z^1, .., z^k)$. Therefore, in terms
+  of $Q'$, we have
+  \begin{equation}
+    -Q' = J^TQ'J
+  \end{equation}
+  where
+  \begin{equation}
+    J = 
+    \left(
+      \begin{matrix}
+        O & -I_k \\
+        I_k & O
+      \end{matrix}
+    \right)
+  \end{equation}
+  is an orthogonal matrix. Therefore
+  \begin{equation}
+    \begin{aligned}
+      det(eI-Q') = 0 &\Leftrightarrow det(eI-J^TQ'J) = 0 \\
+      &\Leftrightarrow det(eI+Q') = 0.      
+    \end{aligned}
+  \end{equation}
+\end{proof}
+
+Now consider a complex manifold $M$ which is bianalytically embedded as a subset
+of $\CC^n$. Let $q$ be a point of $M$.
+
+\begin{asser}
+  The focal points of $(M, q)$ along any normal lines $\mathbb{l}$ ocur in pairs
+  which are situated symmetrically about $q$.
+\end{asser}
+
+\begin{proof}
+
+\end{proof}
 

### 2013-01-16 paper.tex
submmited version

@@
 \usepackage{amssymb}
+\usepackage[all]{xy}
 
@@
 \begin{abstract}
-  This report covers roughly the part I of J. Milnor's book(citation). The main
-  result is the theorem of Morse: every smooth manifold has the same homotopy
-  type of a CW-complex. We prove this theorem by developing the concept of
-  non-degenerate smooth functions, their index at critical points and the
-  correspondence between the index and the dimension of attaching cells. After
-  the main theorem, the existence of non-degenerate smooth functions on
-  manifolds is established, and as an application, an alternating proof of the
-  Lefschetz hyperplane theorem is given.
+  This report covers roughly the part I of J. Milnor's book\cite{Mil}. The main
+  result is the theorem: every smooth manifoldhas the same homotopy type of a
+  CW-complex. We prove this theorem by developing the concept of non-degenerate
+  smooth functions, their index at critical points and the correspondence
+  between the index and the dimension of attaching cells. After the main
+  theorem, the existence of non-degenerate smooth functions on manifolds is
+  established, and as an application, a proof of the Lefschetz hyperplane
+  theorem is given.
 \end{abstract}
@@
   \frac{1}{2}(h_{ij}+h_{ji})$ and get $f = \sum_{i,j}
-  x^ix^j\bar{h}_{ij}$. Moreover, $\bar{h}_{i,j}(0) = \frac{1}{2}\frac{\partial^2
+  x^ix^j\bar{h}_{ij}$. Moreover, $\bar{h}_{ij}(0) = \frac{1}{2}\frac{\partial^2
     f}{\partial x^i \partial x^j}(0)$, so it is non-singular.
@@
 \begin{thm}
+  \label{3.1}
   Suppose $f^{-1}[a,b]$ is compact and contains no critical points of $f$. Then
@@
   \begin{equation}
-    \frac{d f(\phi_t(q))}{dt} = X_{\phi_t q}(f) = +1
-  \end{equation}
-  Hence the correspondence $t \mapsto f(\phi_t(q))$ is linear as long as
-  $f(\phi_t(q)) \in [a,b]$. It follows that $f(\phi_{t}(q)) = t + f(q)$ in a
-  small neighborhood of $0 \in \RR$, where $q \in f^{-1}[a,b]$.
-
-  Consider the diffeomorphism $\phi_{b-a} : M \to M$. By above it's clear
-  that $\phi_{b-a}$ maps $M^a$ diffeomorphically onto $M^b$. This prove the
-  first part of the theorem.
+    \frac{d f(\phi_t(q))}{dt} = X_{\phi_t(q)}(f) = 
+    \langle \rho(grad \:  f), grad \: f \rangle \le 1.
+  \end{equation}
+  Hence the inequality $f(\phi_t(q)) \le t + f(q)$ holds for all $t \in \RR$. It
+
+  Consider the diffeomorphism $\phi_{b-a} : M \to M$. If $p \in M^b$, let $q =
+  \phi_{a-b}(p)$. Then $\phi_{b-a}(q) = p$ and $f(q) = f(\phi_{a-b}(p)) \le
+  a-b+f(p) \le a$. So $\phi_{b-a}$ maps $M^a$ onto $M^b$. It follows that
+  $\phi_{b-a}$ maps $M^a$ diffeomorphically onto $M^b$. This prove the first
+  part of the theorem.
 
@@
 \begin{thm}
+  \label{3.2}
   Let $f: M \to \RR$ be a smooth function and let $p$ be a non-degenerate
@@
 For example, we can define $\mu$ as follows. Let $\mu = \epsilon'
-\frac{\int_x^{2\epsilon} \alpha(t)\alpha(2\epsilon-t)}dt{\int_0^{2\epsilon}
+\frac{\int_x^{2\epsilon} \alpha(t)\alpha(2\epsilon-t)dt}{\int_0^{2\epsilon}
   \alpha(t)\alpha(2\epsilon-t)}dt$, where $2\epsilon > \epsilon' > \epsilon$ and
@@
 \begin{asser}
-  The region $F^{-1}(-\infty, c+\epsilon]$ coincides with the region $M^{c+\epsilon}$.
+  The region $F^{-1}(-\infty, c+\epsilon]$ coincides with the region
+  $M^{c+\epsilon}$.
 \end{asser}
@@
       \frac{\partial F}{\partial \xi} &= -1 - \mu'(\xi+2\eta) < 0 \\
-      \frac{\partial F}{\partial \eta} &= 1 - 2\mu'(\xi+2\eta) ge 1 \\
+      \frac{\partial F}{\partial \eta} &= 1 - 2\mu'(\xi+2\eta) \ge 1 \\
       dF &= \frac{\partial F}{\partial \xi}d\xi+\frac{\partial F}{\partial
@@
 locally compact Hausdorff space, $F^{-1}[c-\epsilon, c+\epsilon]$ is compact.
-Note that $F(p) = c- \mu(0) \le c-\epsilon$. $p \notin F^{-1}[c-\epsilon,
+Note that $F(p) = c- \mu(0) < c-\epsilon$. $p \notin F^{-1}[c-\epsilon,
 c+\epsilon]$. Together with the preceding theorem we get
@@
   \{\epsilon-\mu(\xi+2\eta) \le \xi-\eta \le \epsilon \}$. It does,
-  indeed, since $\epsilon \ge \xi > \xi-t^2\eta > \xi-\eta \ge
-  \epsilon-\mu(\xi+2\eta) \ge \epsilon-\mu(\xi+2t\eta)$.
+  indeed, since $\epsilon \ge \xi \ge \xi-t^2\eta \ge \xi-\eta \ge
+  \epsilon-\mu(\xi+2\eta) \ge \epsilon-\mu(\xi+2t^2\eta)$.
 
@@
     (u^1, .., u^n) \mapsto
-    (u^1, .., u^\lambda, cu^{\lambda+1}, .., cu^n) \in M^{c-\epsilon}
-  \end{equation}
-
-  Then it's easy to calculate $c =
+    (u^1, .., u^\lambda, ku^{\lambda+1}, .., ku^n) \in M^{c-\epsilon}
+  \end{equation}
+
+  Then it's easy to calculate $k =
   (\frac{\xi-\epsilon}{\eta})^{\frac{1}{2}}$. Then the homotopy is simply the
@@
   \begin{equation}
-    s_t = t + (1-t)c.
-  \end{equation}
-
-  Again we check that the homotopy lies entirely in $H$. This is true, since
-  $s_t \in [0,1]$. More precisely, $\xi-s_t^2\eta \ge \xi-\eta \ge
-  \epsilon-\mu$.
+    s_t = t + (1-t)k.
+  \end{equation}
+
+  Again we check that the homotopy lies entirely in $H$. We first note that $s_t
+  \in [0,1]$. Then $\xi-s_t^2\eta \ge \xi-\eta \ge \epsilon-\mu$. Also,
+
+  \begin{equation}
+    \begin{aligned}
+      \xi-s_t^2\eta &= \xi -
+      (t^2+2t(1-t)(\frac{\xi-\epsilon}{\eta})^{1/2}+(1-t)^2\frac{\xi-\epsilon}{\eta})\eta
+      \\
+      &=
+      \xi-t^2\eta-2(t-t^2)\sqrt{\eta(\xi-\epsilon)}-(1-t)^2\epsilon+(1-t)^2\epsilon
+      \\
+      &\le
+      \xi-t^2(\epsilon-\xi)-(2t-2t^2)(\xi-\epsilon)-(1-t)^2\xi+(1-t)^2\epsilon
+      \\
+      &= \epsilon,
+    \end{aligned}
+  \end{equation}
+  where we use the condition $\xi-\eta \le \epsilon$.
 
@@
 \begin{rmk}
+  \label{3.3}
   More generally suppose that there are $k$ non-degenerate critical points
@@
 
+\begin{thm}
+  \label{main}
+  If f is a differentiable function on a manifold $M$ with no degenerate
+  critical points, and if each $M^a$ is compact, then $M$ has the homotopy type
+  of a CW-complex with one cell of dimension $\lambda$ for each critical point
+  of index $\lambda$.
+\end{thm}
+
+The proof will be based on two lemmas concerning a topological space $X$ with a
+cell attached. The first lemma says that if two attaching methods are homotopic
+to each other, then the two resulting spaces are homotopy equivalent. The second
+lemma shows that if the base space is changed by a map preserving its homotopy
+type, then then the two attaching spaces are homotopic equivalent in a natural
+way.
+
 \begin{lem}[Whitehead]
+  \label{whitehead}
   Let $\phi_0$ and $\phi_1$ be homotopic maps from the sphere $\dot{e}^\lambda$
@@
 \end{lem}
+
+\begin{proof}
+  Let $\phi_t$ be the homotopy between $\phi_0$ and $\phi_1$. Let $u$ denote a
+  point on $\dot{e}^\lambda$. We define $k$ by the following formulas:
+  \begin{equation}
+    \begin{array}{lcl}
+      k(x) = x, & x \in X, \\
+      k(tu) = 2tu & t \in [0,\frac{1}{2}], \\
+      k(tu) = \phi_{2-2t}(u) & t \in [\frac{1}{2},1].
+    \end{array}
+  \end{equation}
+
+  Notice that $k(\frac{1}{2}u) = u = \phi_1(u)$.
+
+  Define $l : X \cup_{\phi_1} e^\lambda \to X \cup_{\phi_0} e^\lambda$ in a
+  similar way as $k$:
+
+  \begin{equation}
+    \begin{array}{lcl}
+      k(x) = x, & x \in X, \\
+      k(tu) = 2tu & t \in [0,\frac{1}{2}], \\
+      k(tu) = \phi_{2t-1}(u) & t \in [\frac{1}{2},1].
+    \end{array}
+  \end{equation}
+
+  Then $lk$ is defined as the following formulas
+
+  \begin{equation}
+    \begin{array}{lcl}
+      lk(x) = x, & x \in X, \\
+      k(tu) = 4tu & t \in [0,\frac{1}{4}], \\
+      k(tu) = \phi_{4t-1}(u) & t \in [\frac{1}{4},\frac{1}{2}], \\
+      k(tu) = \phi_{2-2t}(u) & t \in [\frac{1}{1},1].
+    \end{array}
+  \end{equation}
+
+  Hence there is a homotopy between $lk$ and identity
+
+  \begin{equation}
+    \begin{array}{lcl}
+      H(s, x) = x, & s \in [0,1], x \in X,\\
+      H(s, tu) = (4-3s)tu & t \in [0,\frac{1}{4-3s}], \\
+      H(s, tu) = \phi_{4t-1}(u) & t \in [\frac{1}{4-3s},\frac{2-s}{4-3s}], \\
+      H(s, tu) = \phi_{\frac{4-3s}{4}(2-2t)}(u) & t \in [\frac{2-s}{4-3s},1].
+    \end{array}
+  \end{equation}
+
+  $H$ is continuous on a finite number of closed sets of $[0,1]\times[0,1]$ and
+  well-defined, so $H$ is continuous.
+
+  In a similar fashion, we can construct a homotopy from $kl$ to identity
+
+  \begin{equation}
+    \begin{array}{lcl}
+      \bar{H}(s, x) = x, & s \in [0,1], x \in X,\\
+      \bar{H}(s, tu) = (4-3s)tu & t \in [0,\frac{1}{4-3s}], \\
+      \bar{H}(s, tu) = \phi_{2-(4-3s)t}(u) &
+      t \in [\frac{1}{4-3s},\frac{2-s}{4-3s}], \\
+      \bar{H}(s, tu) = \phi_{\frac{(4-3s)t}{2}+\frac{3}{2}s-1}(u) &
+      t \in [\frac{2-s}{4-3s},1].
+    \end{array}
+  \end{equation}
+
+\end{proof}
+
+\begin{lem}
+  \label{3.7}
+  Let $\phi : \dot{e}^\lambda \to X$ be an attaching map. Any homotopy
+  equivalence $f: X \to Y$ extends to a homotopy equivalence
+  \begin{equation}
+    F: X \cup_\phi e^\lambda \to Y \cup_{f\phi} e^\lambda
+  \end{equation}
+\end{lem}
+
+\begin{proof}
+  Define $F|_X = f$, $F|_{e^\lambda} = identity$. Let $g$ be the homotopy
+  inverse of $f$. Define $G: Y \cup_{f\phi} e^\lambda \to X \cup_{gf\phi}
+  e^\lambda$ by $G|_Y = g$, $G|_{e^\lambda} = identity$. Since $gf\phi$ is
+  homotopic to $\phi$, by \ref{whitehead} there is a homotopy equivalence
+  $G: X \cup_{gf\phi} e^\lambda \to X \cup_{\phi} e^\lambda$. We want to show
+  that $kG$ is a homotopic inverse of $F$. We first write down the composition
+  $kGF$ in the following formulas
+
+  \begin{equation}
+    \begin{array}{lcl}
+      kGF(x) = x, & x \in X, \\
+      kGF(tu) = 2tu & t \in [0,\frac{1}{2}], \\
+      kGF(tu) = h_{2-2t}(u) & t \in [\frac{1}{2},1]
+    \end{array}
+  \end{equation}
+  where $h_t$ is a homotopy between $gf$ and identity. $kGF$ is homotopic to
+  identity by the following formulas
+
+  \begin{equation}
+    \begin{array}{lcl}
+      H(s, x) = h_s(x), & s \in [0,1], x \in X,\\
+      H(s, tu) = (2-s)tu & t \in [0,\frac{1}{2}], \\
+      H(s, tu) = h_{2-(2-s)t}(tu) & t \in [\frac{1}{2},1]
+    \end{array}
+  \end{equation}
+
+  Thus $F$ has a left inverse. Note that $g$ and the induced $G$ also satisfy
+  the condition of the lemma. So $G$ also has a left inverse.
+
+  It is elementary that if $F$ has both a left inverse $L$ and a right inverse
+  $R$, then $F$ is a homotopy equivalence and both $L$ and $R$ are two sided
+  inverses.
+
+  Now we have $k(GF) \sim id$. Since $k$ is a homotopy equivalence, $GFk \sim
+  id$. Thus $G$ has a right inverse. Then $G$ is also a homotopy equivalence and
+  $FkG \sim id$. Thus $F$ also has a right inverse. This proves that $F$ is a
+  homotopy equivalence.
+\end{proof}
+
+We now go back to the proof of theorem \ref{main}:
+
+\begin{proof}
+  Let $c_1 < c_2 < c_3 < ..$ be the critical values of $f: M \to \RR$. The
+  sequence ${c_i}$ has no cluster points, for each $M^a$ is compact \footnote{If
+    $c$ is a cluster point of ${c_i}$,then there exists a sequence ${p_j}$ in M
+    such that $f(p_j) = c_{i_j}$ and $\lim_{j \to \infty} p_j = p$ If p is not a
+    critical point, then there is a neighborhood $U$ of $p$ such that each point
+    of $U$ is not a critical point. But this is a contradiction, since $p$ is
+    the limit of the sequence ${p_j}$.}. We first prove by induction that each
+  level set $M^a$ has the homotopy type of a CW-complex. If $a < c_1$, then $M^a
+  = \emptyset$. Suppose $c_{i-1} < a < c_{i} =: c$. By theorems \ref{3.1},
+  \ref{3.2} and \ref{3.3}, $M^{c+\epsilon} = M^a \cup_{\phi_1} e^{\lambda_1}
+  \cup .. \cup_{\phi_{j(c)}} e^{\lambda_{j(c)}}$, for sufficiently small
+  $\epsilon$. By induction hypothesis, there is a homotopy equivalence $h : \to
+  K$.By lemma \ref{3.7}, $h$ induces a homotopy equivalence between
+  $M^{c+\epsilon} = M^a \cup_{\phi_1} e^{\lambda_1} \cup .. \cup_{\phi_{j(c)}}
+  e^{\lambda_{j(c)}}$ and $K \cup_{h\circ\phi_1} e^{\lambda_1} \cup
+  .. \cup_{\circ\phi_{j(c)}} e^{\lambda_{j(c)}}$
+
+  Each $h \circ \phi_j$ is homotopic by cellular approximation to
+  \begin{equation}
+    \psi_j: \dot{e}^{\lambda_j} \to K^{\lambda_j-1}.
+  \end{equation}
+
+  By lemma \ref{whitehead}, replacing the attaching map does not
+  change the homotopy type. Thus we have shown that $M^{c+\epsilon}$
+  has the homotopy type of a CW-complex.
+
+  If M is compact, then $M = M^a$ for some $a \in \RR$ and the proof is done. If
+  M is not compact, but all critical points lie in $M^a$, a proof similar to
+  \ref{3.1} shows that $M^a$ is a deformation retract of $M$.
+
+  If there are infinitely many critical points, then we can construct an
+  infinite sequence of homotopy equivalences
+  \begin{equation*}
+    \xymatrix@C+0em@R+0em{
+      M_{a_1} \ar[d]_{g_1} \ar@{^(->}[r] &
+      M_{a_2} \ar[d]_{g_2} \ar@{^(->}[r]&\cdots \\
+      K_1 \ar@{^(->}[r] & K_2 \ar@{^(->}[r] &\cdots
+    }
+  \end{equation*}
+  each extending the previous one. Let $K = \cup_{i=1}^{\infty}K_i$ have the
+  direct limit topology. We show that $K$ is a CW-complex. Let $C$ be a closed
+  set in $K$. Then by definition, $C\cap K_i$ is closed in $K_i$ for all
+  $i$. This means that $C\cap e_{ij}$ is closed in $e_{ij}$ for all $e_{ij} \in
+  K_i$ for all $i$. Thus $C \cap e$ is closed for all cell in $K$. This proves
+  that $K$ has the weak topology.
+
+  Now let $C$ be a compact set in $K$. Let $I=\{ p_i | p_i \in C \cap
+  e_i\}$, where $e_i$ ranges over all cells in $K$. Then $I$ is
+  closed, since the intersection of $I$ and each cell is a point. $I$
+  is descrete, since each $p \in I$ lies in a cell and each cell is
+  closure-finite. This proves that $K$ has the closure-finite
+  property.
+
+  Let $g: M \to K$ be the limit map. We need Whitehead's theorem to conclude
+  that $g$ is a homotopy equivalence:
+
+  \begin{thm}
+    If $M$ and $K$ are both dominated by CW-complexes, then any map $M \to K$
+    which induces isomorphisms of homotopy groups is a homotopy equivalence.
+  \end{thm}
+
+  \begin{defn}\cite{Hat}
+    A space $Y$ is dominated by a space $X$ if there are maps
+    \begin{equation}
+      \xymatrix{
+        Y \ar[r]^i & X \ar[r]^r & Y
+      }
+    \end{equation}
+    such that $ri \sim 1_Y$.
+  \end{defn}
+
+  $M$ can be dominated by a CW-complex in the following way. Embed $M$ into
+  $\RR^n$. Let $N$ be a tubular neighborhood of $M$. Triangulate $\RR^n$ so that
+  the simplex intersecting $M$ lies entirely in $N$. Collecting all the
+  simplexes and their faces, we get a CW-complex $K$. $M \subset W$. The
+  retraction of the tubular neighborhood into $M$ restricting on $W$ is a
+  retraction on $W$ into $M$. This shows that $M$ is dominated by a CW-complex.
+
+  It remains to show that $g_*$ is an isomorphism of each $\pi_n(M)$ and
+  $\pi_n(K)$. We prove the onto-ness first. Let $f_i$ denote the homotopy
+  inverse of $g_i$. Let $[\phi] \in \pi_n(K)$. Since $\phi(S^n)$ is compact,
+  $\phi(S^n)$ lies in some $K_i$. Since $g_i\circ f_i \circ \phi$ is homotopic
+  to $\phi$ in $K_i \subset K$, $g_*[f_i\circ\phi] = [\phi]$. Next we prove that
+  $g_*$ is one-to-one. Suppose there exist $\phi_0, \phi_1 : S^n \to K$ such
+  that $g\circ\phi_0 \sim g\circ\phi_1$ in $K$. Denote the homotopy as
+  $H$. Since $H$ is continuous and $[0,1]\times S^n$ is compact, the homotopy
+  lies in a compact set of $K$, thus in $K_i$ for some $i$. Therefore $f_i\circ
+  g_i\circ\phi_0 \sim f_i\circ g_i\phi_1$ in $M^{a_i}$. Hence $f_i\circ
+  \phi_0 \sim \phi_1$ in $M$.
+
+  The theorem follows.
+
+\end{proof}
 
@@
 \begin{lem}[Index theorem for $L_p$]
+  \label{index}
+  \label{index_of_Lp}
   The index of $L_p$ at a non-degenerate critical point $q \in M$ is equal to
@@
 \begin{asser}
-  The focal points of $(M, q)$ along any normal lines $\mathbb{l}$ ocur in pairs
+  The focal points of $(M, q)$ along any normal lines occur in pairs
   which are situated symmetrically about $q$.
@@
 \begin{proof}
-
-\end{proof}
+  Let $(z^1, .., z^k)$ be coordinates centered at $q$ such that $g_{ij}(q) =
+  \delta_{ij}$\footnote{
+    Let $E_1, .., E_k$ be an orthornormal basis in $T_qM$. Let $(u_1, .., u_k)$
+    be a local coordinates at $q$. Then $E_i = a_{ji}\frac{\partial w}{\partial
+      u^j}(q)$, where the matrix $(a_{ij})$ is non singular. Define $(v_1, ..,
+    v_k)$ by $u_i = a_{ij}v^j$. Then $\frac{\partial w}{\partial v_k} =
+    \frac{\partial w}{\partial u^j}\frac{\partial u^j}{\partial v^i} = E_i$.}
+  . The embedding determines analytic coordinate functions
+  $w_\alpha(z^1, .., z^k)$, $\alpha = 1, .., n$.  In $\CC^n$, we consider the
+  Hermitian inner product $ v \cdot w = \sum_i v_i\bar{w}_i$.
+
+  Let $v$ be a unit vector in $\CC^n$, orthogonal to $M$ at $q$. We consider the
+  quadratic forms
+
+  \begin{equation}
+    Q(z^1, .., z^k) = 
+    \sum_{i,j} v \cdot \frac{\partial^2 w}{\partial z^i \partial z^j}z^iz^j
+  \end{equation}
+  and
+
+  \begin{equation}
+    \label{QQ}
+    Q'(x^1, .., x^k, y^1, .., y^k) = Re\{Q(z^1, .., z^k)\}
+  \end{equation}
+  where $z^j = x^j+iy^j$.
+
+  We have
+
+  \begin{equation}
+    \begin{aligned}
+      \frac{\partial^2 w}{\partial z^i \partial z^j} &=
+      \frac{1}{4}\left(
+        \frac{\partial}{\partial x^i}-i\frac{\partial}{\partial
+          y^i}\right)\left(\frac{\partial}{\partial
+          x^j}-i\frac{\partial}{\partial y^j}
+      \right)w \\
+      &= \frac{\partial^2 w}{\partial x^i \partial x^j} =
+      -\frac{\partial^2 w}{\partial y^i \partial y^j} = 
+      -i\frac{\partial^2 w}{\partial x^i \partial y^j} = 
+      -i\frac{\partial^2 w}{\partial y^i \partial x^j}
+    \end{aligned}
+  \end{equation}
+  Substituting the above relations into \eqref{QQ}, we find that $Q'$ is exactly
+  the second fundamental form of $M$ at $q$ in $\RR^{2n}$.  Recall that the
+  focal points are exactly $q+K_i^{-1}v$, where $K_i$ are the principal
+  curvatures. From the previous assertion, we see that $-K_i$ is also a
+  principal curvature. Thus the focal points lie symmetrically about $q$ on the
+  line passing through $q$ in the $v$ direction.
+\end{proof}
+
+Now we go back to the proof of the theorem. Choose $p$ in $\CC^n$ such that
+$L_p$ is non-degenerate. Since $M$ is a closed subset of $\CC^n$, each $M^a =
+L_p^{-1}[0, a]$ is compact. For each $q$ there are at most $2k$ focal points
+that lie on line $\stackrel{\leftrightarrow}{pq}$. Since they are distributed
+about $q$, there are at most $k$ focal points that lie on the line segment from
+$q$ to $p$. By lemma \ref{index}, the index of $L_p$ at $q$ is at most $k$. By
+theorem \ref{main}, $M$ has the homotopy type of a CW-complex of dimension at
+most $k$. This completes the proof.
+
+\begin{cor}
+  If $M \subset \CC^n$ is a non-singular affine algebraic variety in $\CC^n$
+  with real dimension $2k$, then
+  \begin{equation}
+    H_i(M; \ZZ) = 0
+  \end{equation}
+  for $i>k$.
+\end{cor}
+
+\begin{proof}
+  $M$ has the homotopy type of a CW-complex of dimension $\le k$. Since $M$ has
+  no cells of dimension $ > k$, the $i$th cellular chain complex is $0$.
+\end{proof}
+
+\begin{cor}[Lefschetz]
+  Let $V$ be an algebraic variety of complex dimension $k$ which lies in the
+  complex projective space $\CC P_n$. Let $P$ be a hyperplane in $\CC P_n$ which
+  contains the singular points (if any) of $V$. Then the inclusion map
+  \begin{equation}
+    V\cup P \to V
+  \end{equation}
+  induces isomorphisms of homology groups in dimensions less than
+  $k-1$. Furthermore, the induced homomorphism
+  \begin{equation}
+    H_k(V\cup P;\ZZ) \to H_{k-1}(V;\ZZ)
+  \end{equation}
+  is onto.
+\end{cor}
+
+\begin{proof}
+  The short exact sequence
+  \begin{equation}
+    \xymatrix{
+      0 \ar[r] &
+      S_{\cdot}(V\cap P;\ZZ) \ar[r] &
+      S_{\cdot}(V;\ZZ) \ar[r] &
+      S_{\cdot}(V, V\cap P;\ZZ) \ar[r] & 
+      0
+    }
+  \end{equation}
+  induces the long exact sequence
+  \begin{equation}
+    \xymatrix{
+      \cdots \ar[r] &
+      H_{r+1}(V, V\cap P;\ZZ) \ar[r] &
+      H_{r}(V\cap P;\ZZ) \ar[r] &
+      H_{r}(V,;\ZZ) \ar[r] & 
+      H_{r}(V, V\cap P;\ZZ) \ar[r] &
+      \cdots
+    }
+  \end{equation}
+
+  Therefore it suffices to show that $H_r(V, V\cap P; \ZZ) = 0$ for $r \le
+  k-1$. The Lefschetz duality theorem asserts that
+  \begin{equation}
+    H_r(V,V\cap P;\ZZ) \cong H^{2k-r}(V-(V\cap P);\ZZ).
+  \end{equation}
+
+  Since $V-(V\cap P)$ is a complex analytic manifold embedded as a closed set in
+  $\CC^n$, it has the homotopy type of a CW-complex of dimension $\le
+  k$. Therefore, by the previous corollary, $H_{2k-r}(V-(V\cap P);\ZZ) = 0$ for
+  $r \le k-1$.
+\end{proof}
+
+\begin{thebibliography}{9}                                                                                                
+%\bibitem{Car} \textsc{Carmo, M. do},\ \textit{Riemannian Geometry}, Birkh\"auser, 1992.
+
+\bibitem{Mil} \textsc{Milnor, J.},\ \textit{Morse Theory}, Princeton University
+  Press, 1969.
+
+\bibitem{Hat} \textsc{Hatcher, A.},\ \textit{Algebraic Topology}, Cambridge
+  University Press, 2002.
+
+\bibitem{Spa} \textsc{Spanier, E.},\ \textit{Algebraic Topology}, McGraw-Hill,
+  1966.
+
+\end{thebibliography}
 
